### 2014-06-21 2/literature_review.tex
auto

SAR speckle phenomena are explained as the interference of many coherent but dephased backscattering components;
  each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
The random nature of the SAR data arises
  due to the unknown and varying location, height and thus distance of each elementary scatterer;
  which, in turn, generates random phases in their back-scattering responses.
Assuming the number of these elementary back scatterers is sufficiently large,
  then the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}.
Consequently the interference of these randomly phased responses can be considered as
  a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  
Specifically the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as
  random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. 
Their probability density functions (PDF) are given as:

\begin{equation}
\label{eqn:SAR Real and Imaginary Components PDF}
\caption{eqn:SAR Real and Imaginary Components PDF}
pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{\left( \frac{A_x^2}{\sigma^2} \right) }
\end{equation}

@@

\subsubsection{The Polarization Basis Transformation}

Assuming that the polarization states are known, the wave representation can be given in terms of $\xi_x$ and $\xi_y$ as:%****IVM, you need to mention A_0.... as well as \phi
\begin{equation*}
\left( 
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right) 
= A_0 e^{-i \phi_0} \left(
\begin{array}{c c}
 \cos(\Psi) & -\sin(\Psi) \\
 \sin(\Psi) & \cos(\Psi)
\end{array}
\right) 
\left(
\begin{array}{c}
 \cos(\chi) \\
 i \sin(\chi)
\end{array}
\right) 
\end{equation*}
The representation of a wave, however, depends on the choice of orthogonal reference frame basis.

Consider two different orthogonal basis, $\{ x,y \}$ and $\{ h,v \}$.
A given Jones vector can be measured in both basis as:
$J_{xy}= 
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right) $ and 
$J_{hv}
= \left(
\begin{array}{c}
 \xi_h \\
 \xi_v
\end{array}
\right)$ê
.
The transformation from $\{h,v\}$ to $\{x,y\}$ is governed by a unitary transformation matrix $U_2$, which is given as:
\begin{equation*}
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)
= U_2
\left(
\begin{array}{c}
 \xi_h \\
 \xi_v
\end{array}
\right)
\end{equation*}

Boerner \cite{Boerner_1991_ProcsIEEE} has given $U_2$ as:
\begin{equation*}
U_2 = \frac{1}{\sqrt{1+\rho\rho^*}}
\left(
\begin{array}{c c}
 1 & -\rho^* \\
 \rho & 1
\end{array}
\right)
\left(
\begin{array}{c c}
 e^{-i\delta} & 0 \\
 0 & e^{i\delta}
\end{array}
\right)
\end{equation*}
where
	$\rho$ is the complex polarisation ratio of the Jones vector for the first new basis, and
	$\delta = \tan^{-1}(\tan(\Psi) \tan(\chi)) - \phi_0$ is the phase reference for the new basis, 
	and $\delta$ is required for the determination of the initial phase of the Jones vector in the new reference basis.

In the same vein, \cite{Pottier_2008_IGARSS} gives %****IVM pls change this to a proper \cite{}
\begin{equation*}
U_2 = \left(
\begin{array}{c c}
 \cos(\Psi) & -\sin(\Psi) \\
 \sin(\Psi) & \cos(\Psi)
\end{array}
\right)
\left(
\begin{array}{c c}
 \cos(\chi) & i\sin(\chi) \\
 i\sin(\chi) & \cos(\chi)
\end{array}
\right)
\left(
\begin{array}{c c}
 e^{-i \phi_0} & 0 \\
 0 & e^{i \phi_0}
\end{array}
\right)    
\end{equation*}

From these results, it is then possible to derive equations for the transformation of the scattering matrix.
Noting that by definition, $J_{xy}^r=S_{xy} J_{xy}^t$, $J_{hv}^r=S_{hv} J_{hv}^t$ 
and that $J_{xy}^*= U_2 J_{hv}^*$, also that $(U_2)^{-1} = (U_2)^T$,
it is then trivial to show that:
\begin{equation*}
S_{xy} = U_2 S_{hv} U_2^T
\end{equation*}

%***IVM: again, I think you need to introduce some of the variables below, like delta, rho. Is rho* the complex conjugate? Better to mention that too....
Using the result above, we then have:
\begin{equation*}
S_{xx} = \frac{1}{1+\rho \rho^*} 
\left( 
S_{HH} e^{-2i\delta} - \rho^* (S_{HV}+S_{VH}) + (\rho^*)^2 S_{VV} e^{2i\delta}
\right)
\end{equation*}
\begin{equation*}
S_{xy} = \frac{1}{1+\rho \rho^*} 
\left( 
\rho S_{HH} e^{-2i\delta} + S_{HV} -\rho \rho^* S_{VH} - \rho^* S_{VV} e^{2i\delta}
\right)
\end{equation*}
\begin{equation*}
S_{yx} = \frac{1}{1+\rho \rho^*} 
\left( 
\rho S_{HH} e^{-2i\delta} - \rho \rho^* S_{HV} + S_{VH} - \rho^* S_{VV} e^{2i\delta}
\right)
\end{equation*}
\begin{equation*}
S_{yy} = \frac{1}{1+\rho \rho^*} 
\left( 
\rho^2 S_{HH} e^{-2i\delta} + \rho (S_{HV} + S_{VH}) + S_{VV} e^{2i\delta}
\right)
\end{equation*}

In the case of mono-static POLSAR, i.e. $S_{HV}=S_{VH}=S_{XX}$ and $S_{xy}=S_{yx}$, the equations become
\begin{equation*}
S_{xx} = \frac{1}{1+\rho \rho^*} 
\left( 
S_{HH} e^{-2i\delta} - 2 \rho^* S_{XX} + (\rho^*)^2 S_{VV} e^{2i\delta}
\right)
\end{equation*}
\begin{equation*}
S_{yx} = S_{xy}= \frac{1}{1+\rho \rho^*} 
\left( 
\rho S_{HH} e^{-2i\delta} + (1-\rho \rho^*) S_{XX} - \rho^* S_{VV} e^{2i\delta}
\right)
\end{equation*}
\begin{equation*}
S_{yy} = \frac{1}{1+\rho \rho^*} 
\left( 
\rho^2 S_{HH} e^{-2i\delta} + 2 \rho S_{XX} +  S_{VV} e^{2i\delta}
\right)
\end{equation*}

The results here, together with Stokes Vector's formula, can be used to prove the following identity,
  which can form the basis of a novel approach in POLSAR speckle filtering: %used throughout this thesis:
\begin{equation*}
S_t = 
\left(
	\begin{array} {c}
		S_hS_h + S_vS_v \\
		S_hS_h - S_vS_v \\
		2 \Re{(S_hS_v^*)} \\
		2 \Im{(S_hS_v^*)}
	\end{array}
\right)
= 
\left(
	\begin{array} {c}
		S_hS_h + S_vS_v \\
		S_hS_h - S_vS_v \\
		S_+S_+ - S_-S_- \\
		S_lS_l - S_rS_r
	\end{array}
\right)
\end{equation*}
where $S_t$ is the Stokes vector and $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ are the intensity of received signals in $+45^o$ linear, $-45^o$ linear, right circular and left circular polarization respectively.

%The transformation from $\{h,v\}$ to $\{+\pi/4,-\pi/4\}$ as well as from $\{h,v\}$ to circular basis $\{l,r\}$ are special cases of the above formula.
%Ignoring the determination of initial phases, we have: 
%	the measured signal at $\pi/4$ linear polarizer / projection as: $\xi_+ = \frac{\xi_h + \xi_v}{\sqrt{2}}$,
%	at $-\pi/4$ linear polarizer as: $\xi_- = \frac{\xi_h - \xi_v}{\sqrt{2}}$, 
%	at left circular polarization as: $\xi_l = \frac{\xi_h + i \xi_v}{\sqrt{2}}$, 
%	and at right circular polarization as $\xi_r = \frac{\xi_h - i \xi_v}{\sqrt{2}}$.
%
%The Stokes vectors, when aligned at these transformed projections are given by the following well-known equations
%\begin{equation}
%S_t = \left(
%\begin{array}{c}
% |\xi_h|^2 + |\xi_v|^2 \\
% |\xi_h|^2 - |\xi_v|^2 \\
% 2 \Re( \xi_h \xi_v^* ) \\
% 2 \Im( \xi_h \xi_v^* ) 
%\end{array}
%\right)
%= \left(
%\begin{array}{c}
% |\xi_+|^2 + |\xi_-|^2 \\
% -2 \Re( \xi_+^* \xi_- ) \\
% |\xi_+|^2 - |\xi_-|^2 \\
% 2 \Im( \xi_+^* \xi_- ) 
%\end{array}
%\right)
%= \left(
%\begin{array}{c}
% |\xi_l|^2 + |\xi_r|^2 \\
% 2 \Re( \xi_l^* \xi_r ) \\
% -2 \Im( \xi_l^* \xi_r ) \\ 
% |\xi_l|^2 - |\xi_r|^2 
%\end{array}
%\right)  
%\end{equation}

>>>>

SAR speckle phenomena are explained as the interference of many coherent but dephased backscattering components;
  each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
The random nature of the SAR data arises
  due to the unknown and varying location, height and thus distance of each elementary scatterer;
  which, in turn, generates random phases in their back-scattering responses.
%Assuming the number of these elementary back scatterers is sufficiently large,
Assuming these elementary back-scatterers are large in number and independent in nature,  
  then the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}.
Consequently the interference of these randomly phased responses can be considered as
  a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  
Specifically the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as
  random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. 
Their probability density functions (PDF) are given as:

\begin{equation}
\label{eqn:SAR Real and Imaginary Components PDF}
\caption{eqn:SAR Real and Imaginary Components PDF}
pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{- \left( \frac{A_x^2}{\sigma^2} \right) }
\end{equation}

@@

%\subsubsection{The Polarization Basis Transformation}
%Assuming that the polarization states are known, the wave representation can be given in terms of $\xi_x$ and $\xi_y$ as:%****IVM, you need to mention A_0.... as well as \phi
%\left( 
%\begin{array}{c}
% \xi_x \\
% \xi_y
%\end{array}
%\right) 
%= A_0 e^{-i \phi_0} \left(
%\begin{array}{c c}
% \cos(\Psi) & -\sin(\Psi) \\
% \sin(\Psi) & \cos(\Psi)
%\end{array}
%\right) 
%\left(
%\begin{array}{c}
% \cos(\chi) \\
% i \sin(\chi)
%\end{array}
%\right) 
%The representation of a wave, however, depends on the choice of orthogonal reference frame basis.
%Consider two different orthogonal basis, $\{ x,y \}$ and $\{ h,v \}$.
%A given Jones vector can be measured in both basis as:
%$J_{xy}= 
%\left(
%\begin{array}{c}
% \xi_x \\
% \xi_y
%\end{array}
%\right) $ and 
%$J_{hv}
%= \left(
%\begin{array}{c}
% \xi_h \\
% \xi_v
%\end{array}
%\right)$ê
%.
%The transformation from $\{h,v\}$ to $\{x,y\}$ is governed by a unitary transformation matrix $U_2$, which is given as:
%\left(
%\begin{array}{c}
% \xi_x \\
% \xi_y
%\end{array}
%\right)
%= U_2
%\left(
%\begin{array}{c}
% \xi_h \\
% \xi_v
%\end{array}
%\right)
%Boerner \cite{Boerner_1991_ProcsIEEE} has given $U_2$ as:
%U_2 = \frac{1}{\sqrt{1+\rho\rho^*}}
%\left(
%\begin{array}{c c}
% 1 & -\rho^* \\
% \rho & 1
%\end{array}
%\right)
%\left(
%\begin{array}{c c}
% e^{-i\delta} & 0 \\
% 0 & e^{i\delta}
%\end{array}
%\right)
%where
%	$\rho$ is the complex polarisation ratio of the Jones vector for the first new basis, and
%	$\delta = \tan^{-1}(\tan(\Psi) \tan(\chi)) - \phi_0$ is the phase reference for the new basis, 
%	and $\delta$ is required for the determination of the initial phase of the Jones vector in the new reference basis.
%In the same vein, \cite{Pottier_2008_IGARSS} gives %****IVM pls change this to a proper \cite{}
%U_2 = \left(
%\begin{array}{c c}
% \cos(\Psi) & -\sin(\Psi) \\
% \sin(\Psi) & \cos(\Psi)
%\end{array}
%\right)
%\left(
%\begin{array}{c c}
% \cos(\chi) & i\sin(\chi) \\
% i\sin(\chi) & \cos(\chi)
%\end{array}
%\right)
%\left(
%\begin{array}{c c}
% e^{-i \phi_0} & 0 \\
% 0 & e^{i \phi_0}
%\end{array}
%\right)    
%From these results, it is then possible to derive equations for the transformation of the scattering matrix.
%Noting that by definition, $J_{xy}^r=S_{xy} J_{xy}^t$, $J_{hv}^r=S_{hv} J_{hv}^t$ 
%and that $J_{xy}^*= U_2 J_{hv}^*$, also that $(U_2)^{-1} = (U_2)^T$,
%it is then trivial to show that:
%S_{xy} = U_2 S_{hv} U_2^T
%%***IVM: again, I think you need to introduce some of the variables below, like delta, rho. Is rho* the complex conjugate? Better to mention that too....
%Using the result above, we then have:
%S_{xx} = \frac{1}{1+\rho \rho^*} 
%\left( 
%S_{HH} e^{-2i\delta} - \rho^* (S_{HV}+S_{VH}) + (\rho^*)^2 S_{VV} e^{2i\delta}
%\right)
%S_{xy} = \frac{1}{1+\rho \rho^*} 
%\left( 
%\rho S_{HH} e^{-2i\delta} + S_{HV} -\rho \rho^* S_{VH} - \rho^* S_{VV} e^{2i\delta}
%\right)
%S_{yx} = \frac{1}{1+\rho \rho^*} 
%\left( 
%\rho S_{HH} e^{-2i\delta} - \rho \rho^* S_{HV} + S_{VH} - \rho^* S_{VV} e^{2i\delta}
%\right)
%S_{yy} = \frac{1}{1+\rho \rho^*} 
%\left( 
%\rho^2 S_{HH} e^{-2i\delta} + \rho (S_{HV} + S_{VH}) + S_{VV} e^{2i\delta}
%\right)
%In the case of mono-static POLSAR, i.e. $S_{HV}=S_{VH}=S_{XX}$ and $S_{xy}=S_{yx}$, the equations become
%S_{xx} = \frac{1}{1+\rho \rho^*} 
%\left( 
%S_{HH} e^{-2i\delta} - 2 \rho^* S_{XX} + (\rho^*)^2 S_{VV} e^{2i\delta}
%\right)
%S_{yx} = S_{xy}= \frac{1}{1+\rho \rho^*} 
%\left( 
%\rho S_{HH} e^{-2i\delta} + (1-\rho \rho^*) S_{XX} - \rho^* S_{VV} e^{2i\delta}
%\right)
%S_{yy} = \frac{1}{1+\rho \rho^*} 
%\left( 
%\rho^2 S_{HH} e^{-2i\delta} + 2 \rho S_{XX} +  S_{VV} e^{2i\delta}
%\right)
%The results here, together with Stokes Vector's formula, can be used to prove the following identity,
%  which can form the basis of a novel approach in POLSAR speckle filtering: %used throughout this thesis:
%S_t = 
%\left(
%	\begin{array} {c}
%		S_hS_h + S_vS_v \\
%		S_hS_h - S_vS_v \\
%		2 \Re{(S_hS_v^*)} \\
%		2 \Im{(S_hS_v^*)}
%	\end{array}
%\right)
%= 
%\left(
%	\begin{array} {c}
%		S_hS_h + S_vS_v \\
%		S_hS_h - S_vS_v \\
%		S_+S_+ - S_-S_- \\
%		S_lS_l - S_rS_r
%	\end{array}
%\right)
%where $S_t$ is the Stokes vector and $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ are the intensity of received signals in $+45^o$ linear, $-45^o$ linear, right circular and left circular polarization respectively.
%%The transformation from $\{h,v\}$ to $\{+\pi/4,-\pi/4\}$ as well as from $\{h,v\}$ to circular basis $\{l,r\}$ are special cases of the above formula.
%%Ignoring the determination of initial phases, we have: 
%%	the measured signal at $\pi/4$ linear polarizer / projection as: $\xi_+ = \frac{\xi_h + \xi_v}{\sqrt{2}}$,
%%	at $-\pi/4$ linear polarizer as: $\xi_- = \frac{\xi_h - \xi_v}{\sqrt{2}}$, 
%%	at left circular polarization as: $\xi_l = \frac{\xi_h + i \xi_v}{\sqrt{2}}$, 
%%	and at right circular polarization as $\xi_r = \frac{\xi_h - i \xi_v}{\sqrt{2}}$.
%%
%%The Stokes vectors, when aligned at these transformed projections are given by the following well-known equations
%%\begin{equation}
%%S_t = \left(
%%\begin{array}{c}
%% |\xi_h|^2 + |\xi_v|^2 \\
%% |\xi_h|^2 - |\xi_v|^2 \\
%% 2 \Re( \xi_h \xi_v^* ) \\
%% 2 \Im( \xi_h \xi_v^* ) 
%%\end{array}
%%\right)
%%= \left(
%%\begin{array}{c}
%% |\xi_+|^2 + |\xi_-|^2 \\
%% -2 \Re( \xi_+^* \xi_- ) \\
%% |\xi_+|^2 - |\xi_-|^2 \\
%% 2 \Im( \xi_+^* \xi_- ) 
%%\end{array}
%%\right)
%%= \left(
%%\begin{array}{c}
%% |\xi_l|^2 + |\xi_r|^2 \\
%% 2 \Re( \xi_l^* \xi_r ) \\
%% -2 \Im( \xi_l^* \xi_r ) \\ 
%% |\xi_l|^2 - |\xi_r|^2 
%%\end{array}
%%\right)  
%%\end{equation}
